A Search for Supernova Remnants in NGC\,6946

### 2018-11-04 ms.tex
Small changes
Description of tables

\todo[inline]{Why is ref for this table not picked up?  We need to describe the table in the text here.}

@@

The data were processed using standard procedures for bias subtraction, flat-fielding, wavelength calibration, and flux calibration (based on baseline GMOS observations of a few spectrophotometric standard stars) from the {\tt gemini} package in IRAF.\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.}  During the processing, the 2-D spectra from different slitlets were separated to give individual 2-D spectra from each slitlet.   We examined each of these individually and selected the object region, as well as one or more sky background regions,  stripped out 1-D spectra of each, and then subtracted the sky spectrum from the corresponding object to obtain the final object spectra.
  Many of the objects are located in regions with bright surrounding galactic background (both continuum and emission lines) from NGC\,6946, so the ability to choose a representative  local background was often a source of uncertainty.   {\bf [Knox, you should edit this paragraph if necessary.]}
%summed the rows containing each object to give  flux-calibrated 1-D spectra.

@@

Table \ref{table_snr_spec}  lists all the SNR candidates for which we obtained spectra.

\todo[inline]{The table needs to be described.  Tables 3 \& 4 need to be modified with longtable, or something, so they will carry over to multiple pages.}

\section{Discussion}
Here are some figures we may wish to show, and points we may want to discuss (note: KSL has done some of these figures on Evernote; those all show \oiii-selected objects, which we may choose to omit):
\begin{enumerate}
    \item Correlation between flux from spectra vs imaging (M83 paper, fig 5)
    \item \sii:\ha\ ratio vs \ha\ flux; \sii:\ha\ ratio vs GC distance (fig for this already here)
    \item We don't give any diameter values for objects.  WIYN data are not great for this, but may be worth something.  Also, aren't there WFC3 Pa$\beta$(?) images; are these useful for getting diameters? There are also a handful of \ha\ images (from ACS or WFC2) which should be useful.  If we are to use these, we need to add another short subsection under Observations.
    \item \hb:\ha\ ratio vs GC Distance: done in Evernote; this indicates that reddening is severe throughout \gal, and is most severe near the center.  Happily, this has little effect on the relative strengths of the most interesting lines: \oi, \ha, \nii, and \sii.
    \item Gradients: \nii:\ha\ and \sii:\ha\ vs GCD (M83 paper, fig 8)
    \item Comparison to shock models (see existing figure).  This appears to indicate abundances between that of LMC and that of the Galaxy (?)
    \item Also compare these same ratios with other galaxies? (M83 paper, Fig 10)
    \item Separate discussion of historical SNe.  SN1980K and SN2004et are both detected, and both show broad lines.  We see NO evidence for nebular  emission from the other historical SN sites.  See Fig.~\ref{historical_SNe}.
\end{enumerate}

>>>>

@@

The data were processed using standard procedures for bias subtraction, flat-fielding, wavelength calibration, and flux calibration (based on baseline GMOS observations of a few spectrophotometric standard stars) from the {\tt gemini} package in IRAF.\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.}  During the processing, the 2-D spectra from different slitlets were separated to give individual 2-D spectra from each slitlet.   We examined each of these individually and selected the object region, as well as one or more sky background regions,  stripped out 1-D spectra of each, and then subtracted the sky spectrum from the corresponding object to obtain the final object spectra.
  Many of the objects are located in regions with bright surrounding galactic background (both continuum and emission lines) from NGC\,6946, so the ability to choose a representative  local background was often a source of uncertainty.  
  We then performed  fits to obtain emission line fluxes  from the spectra.  For these fits, we assumed Gaussian profiles.  We performed fits for various lines and line complexes, specifically for \hb alone, for the [O III] doublet, for the [O I] doublet, for the \ha-[N II] region, and  for the [S II] doublet. For the fits, we assumed that the background varied linearly with wavelength around each line, and that the FWHM of the lines in each line in a complex was the same.

  %summed the rows containing each object to give  flux-calibrated 1-D spectra.

@@

Table \ref{table_snr_spec}  lists the information we obtained for the SNR candidates for which we obtained spectra.    Specifically we list (1) the source name, (2) the extracted  \ha\ flux, (3-9) ratios of various emission lines to \ha\ taken to be 300, (10) the total [SII]:\ha\ ratio and (11) the measured FWHM of the lines in the \ha-[N II] complex.  For doublets, where the line ratio is constrained by atomic physics, that is [O III], [O I], and [N II], we have listed only the stronger line.  We visually inspected all of the spectra and the fits to them; values which we judge to be more uncertain are shown as approximate.  No allowance has been made for systematic errors associated with difficulties in background subtraction.  A number of the objects were observed several times, sometimes with different slit orientations.  In these cases, we report the spectrum which we judge to be the most accurate.  The spectrum used is listed in Table \ref{table_candidates}, where 05.18 should be interpreted as slit number 18 in mask 5.

\section{Discussion}
Here are some figures we may wish to show, and points we may want to discuss (note: KSL has done some of these figures on Evernote; those all show \oiii-selected objects, which we may choose to omit):
\begin{enumerate}
    \item Correlation between flux from spectra vs imaging (M83 paper, fig 5)
    \item \sii:\ha\ ratio vs \ha\ flux; \sii:\ha\ ratio vs GC distance (fig for this already here)
    \item We don't give any diameter values for objects.  WIYN data are not great for this, but may be worth something.  Also, aren't there WFC3 Pa$\beta$(?) images; are these useful for getting diameters? There are also a handful of \ha\ images (from ACS or WFC2) which should be useful.  If we are to use these, we need to add another short subsection under Observations.
    \item \hb:\ha\ ratio vs GC Distance: done in Evernote; this indicates that reddening is severe throughout \gal, and is most severe near the center.  Happily, this has little effect on the relative strengths of the most interesting lines: \oi, \ha, \nii, and \sii.
    \item Gradients: \nii:\ha\ and \sii:\ha\ vs GCD (M83 paper, fig 8)
    \item Comparison to shock models (see existing figure).  This appears to indicate abundances between that of LMC and that of the Galaxy (?)
    \item Also compare these same ratios with other galaxies? (M83 paper, Fig 10)
    \item Separate discussion of historical SNe.  SN1980K and SN2004et are both detected, and both show broad lines.  We see NO evidence for nebular  emission from the other historical SN sites.  See Fig.~\ref{historical_SNe}.
    \item Comparison to MF97
    \item Comparison to Lacey and X-rays catalog and Bruuseman
\end{enumerate}
